Modeling potential JCPOA diversion scenarios with Cyclus

### 2018-05-15 paper.tex
add uncertainty measurement description

@@

All uncertainty have been computed as the standard deviation over over all the
calculations in a single set.

>>>>

In this works, a time step of 1 month have been considered.

@@

In the following, each total uncertainty is reported at $\pm1\sigma$ around the
mean values of the corresponding uncertainty set at each time step. The time
dependant relative uncertainty are computed as the standard deviation of a
single set over its mean value at the corresponding time.
